Together, Individuals Make a Difference

### 2025-01-27 论文/PAPER.tex
论文

    \textbf{PCA}\\
    \%\\
    % 关键字Keywords
    \vspace{5pt}
    \textbf{Keywords}: \textbf{ A, B, C,  }

@@

% 正文开始
\section{Introduction}
\subsection{Problem Background}

\subsection{Restatement of Problem}
A literatrue\cite{1} say something about this problem ...
There is a conception named "momentum" in tennis, which has a great impact on players' performance. It is a generalization of the influence in manifold aspects like mental stress and residual energy. So the fluctuation of momentum is the most probable factor that reveals the trend of match. However,the momentum is not easy to be quantified for it includes many subjective indicators, and there are few models that can be directly used, so we decide to cut in the following questions from statistical analysis and data procession:

\begin{itemize}
	\setlength{\parsep}{0ex} %段落间距
	\setlength{\topsep}{2ex} %列表到上下文的垂直距离
	\setlength{\itemsep}{1ex} %条目间距
	\item Develop a model that captures the flow of play as points occur and apply it to one or more of the matches. Your model should identify which player is performing better at a given time in the match, as well as how much better they are performing. Provide a visualization based on your model to depict the match flow. \textit{Note: in tennis, the player serving has a much higher probability of winning the point/game. You may wish to factor this into your model in some way.}
	\item A tennis coach is skeptical that “momentum” plays any role in the match. Instead, he postulates that swings in play and runs of success by one player are random. Use your model/metric to assess this claim.
	\item Coaches would love to know if there are indicators that can help determine when the flow of play is about to change from favoring one player to the other.
	\begin{itemize}
		\item[1)]
		Using the data provided for at least one match, develop a model that predicts these swings in the match. What factors seem most related (if any)?
	\end{itemize}
	\begin{itemize}
		\item[2)]
		Given the differential in past match “momentum” swings how do you advise a player going into a new match against a different player?
	\end{itemize}
	\item Test the model you developed on one or more of the other matches. How well do you predict the swings in the match? If the model performs poorly at times, can you identify any factors that might need to be included in future models? How generalizable is your model to other matches (such as Women’s matches), tournaments, court surfaces, and other sports such as table tennis.
	\item Produce a report of no more than 25 pages with your findings and include a one- to two-page memo summarizing your results with advice for coaches on the role of“momentum”, and how to prepare players to respond to events that impact the flow of play during a tennis match.
\end{itemize}

@@

$$G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X$$

\begin{figure}[htbp]
	\centering
	\includegraphics[width=12cm]{img/Level1.png}
	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
	\label{fig:aa}
\end{figure}

@@

\section{Task4}

@@

\section{Model Evaluation}
\subsection{Strengths}
1.\\
2.\\
3.\\
4.\\
\subsection{Weaknesses}
1.

\section{Conclusion}
\begin{itemize}
	\item Task1\\
	\qquad

	\item Task2\\
	\qquad
	\item Task3\\
	\qquad

	\item Task4\\
	\qquad

>>>>

    \textbf{PCA}\\

    % 关键字Keywords
    \vspace{5pt}
    \textbf{Keywords}: \textbf{ A, B, C,  }

@@

% 正文开始
\section{Introduction}
\subsection{Problem Background}
During the 2024 Paris Summer Olympics, fans not only paid attention to the individual events but also showed significant interest in the the ranking of countries on the overall medal count and  gold medal table. Ultimately, the United States topped the medal table with a total of 126 medals, while China and the United States shared the top position on the gold medal table, each securing 40 golds. The host country, France, ranked fifth on the gold medal table with 16 gold medals, but finished fourth in the total medal count. Great Britain ranked seventh on the gold medal table with 14 golds, while securing third place in the overall medal count. Despite the prominence of the leading countries, the medal achievements of other nations also attracted attention. For example, Albania, Cape Verde, Dominica, and Saint Lucia each won their first-ever Olympic medal in this edition of the Games, with Dominica and Saint Lucia each earning another gold medal. However, over 60 countries have yet to win a medal in the history of the Olympics.

\subsection{Restatement of Problem}
While predictions of the final medal counts at the Olympics are common, such forecasts are generally not based on historical medal tables. Instead, they are typically made before the start of the upcoming Olympic Games, once the list of competing athletes is known.To clarify the task, the problem is restated as follows:

\begin{itemize}
	\setlength{\parsep}{0ex} %段落间距
	\setlength{\topsep}{2ex} %列表到上下文的垂直距离
	\setlength{\itemsep}{1ex} %条目间距
	\item Develop a model for each country’s medal count, which should at least include the number of gold medals and the total medal count, and estimate the uncertainty/precision of the model,also evaluate its performance.
		\begin{itemize}
		\item[1)]
	Using the model, predict the medal standings for the 2028 Los Angeles Summer Olympics, including prediction intervals for all outcomes. Based on the model’s predictions, identify which countries are most likely to improve their performance and which countries are expected to perform worse than in the 2024.
	\end{itemize}
	\begin{itemize}
		\item[2)]
		The developed model should include countries that have not yet won any medals, while also predicting the number of countries likely to win their first medal in the upcoming Olympics and provide odds for this estimate.
	\end{itemize}
		\begin{itemize}
		\item[3)]
	The model should also consider the number and types of events in each specific Olympic Games, exploring the relationship between the events and the number of medals won by each country. For each country, determine which events are most crucial and why, as well as the impact of the country’s selected events on the results.
	\end{itemize}

	\item In contrast to athletes, who must change their citizenship in order to represent different countries in competitions, coaches do not need to change their citizenship to coach, which makes it easier for them to move to other countries. As a result, the “Great Coach” effect may arise. For example, Lang Ping has coached the volleyball teams of both China and the U.S., leading both to championships, while Bela Karolyi coached the Romanian and U.S. women’s gymnastics teams, achieving great success. The task is to identify evidence in the data that may suggest changes driven by the "Great Coach" effect and estimate its impact on the medal count. Select three countries, determine the events in which they should consider investing in "outstanding" coaches, and estimate the potential impact of such investments.
	\item Explain the unique insights regarding Olympic medal counts that are included in the developed model and how these insights can provide valuable information to the National Olympic Committees of various countries.

@@

\begin{equation}
G_{i} \cap G_{j}=\emptyset, \bigcup_{i=1}^{5} G_{i}=X
\end{equation}
\begin{figure}[htbp]
	\centering
	\includegraphics[width=12cm]{img/Level1.png}
	\caption{Scatter plot of national level classification (based on Kmeans++clustering algorithm)}
	\label{fig:aa}
\end{figure}

@@

	\begin{equation}
		\phi_i(f) = \sum_{S \subseteq N \setminus \{i\}} \frac{|S|!(|N| - |S| - 1)!}{|N|!} [f(S \cup \{i\}) - f(S)]
	\end{equation}

$\phi_i(f)$

@@

\section{Model Evaluation}
\subsection{Strengths}
1.

2.

3.

4. 
\subsection{Weaknesses}
1.

\section{Conclusion}
\begin{itemize}
	\item Task1

	 \qquad AA\\
	bbb

	\item Task2\\
	\qquad AAA
	\item Task3\\
	\qquad AAA

	\item Task4\\
	\qquad AAA
